Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-14 cvpr2018.tex
1th method

where $Y$ and $\bm z$ denotes training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN loss, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.

>>>>

where $Y$ and $\bm z$ denotes training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.
